taxize: taxonomic search and retrieval in R

### 2013-10-01 f1000_rev/taxize_appC.Rnw
Linux is ready to build r-packages.

\section*{Installation of the development version of taxize and API keys}

@@

\begin{itemize}
  \item On Windows, download and install Rtools: http://cran.r-project.org/bin/windows/Rtools/. This is not an R package.
  \item On Mac, make sure you have either XCode (free, available in the app store) or the "Command Line Tools for Xcode" (needs a free apple id, available from http://developer.apple.com/downloads)
  \item On Linux, make sure you've installed not only R, but the R development devtools. This a linux package called something like r-base-dev.
\end{itemize}

>>>>

\documentclass[letterpaper,superscriptaddress,showkeys,longbibliography]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
    colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

\begin{document}
<<setup, include=FALSE, cache=FALSE, size='scriptsize'>>=
## set global chunk options
opts_chunk$set(fig.align='center', fig.show='hold', par=TRUE, warning=FALSE, message=FALSE, error=FALSE, comment='#')
@
\section*{Appendix C. Installation of the development version of taxize and API keys}

@@

\begin{itemize}
  \item On Windows, download and install Rtools: http://cran.r-project.org/bin/windows/Rtools/. This is not an R package.
  \item On Mac, make sure you have either XCode (free, available in the app store) or the "Command Line Tools for Xcode" (needs a free apple id, available from http://developer.apple.com/downloads)
\end{itemize}
